Solar wind predictions for the Parker Solar Probe orbit

### 2017-08-24 paperMVVB/sections/content.tex
fig 10 fix; added version without figures

We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}.
\begin{figure*}
	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_d_plot.pdf}
	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region. The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas). Note that there is a time lag to the SSN depending on the solar wind parameter. Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Wang2000} and \citet{Sheeley1997}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
	\label{fig:sw_extrapolation_ssn_d_plot}
\end{figure*}

@@

However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}. The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}). The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).

>>>>

We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
\begin{figure*}
	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_e_plot.pdf}
	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region. The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas). Note that there is a time lag to the SSN depending on the solar wind parameter. Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Wang2000} and \citet{Sheeley1997}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
	\label{fig:sw_extrapolation_ssn_e_plot}
\end{figure*}

@@

However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}. The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}). The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
